---
title:  -Ad smart
output:
  pdf_document:
    toc: true
    toc_depth: 2
editor_options: 
  markdown: 
    wrap: 72
---

In this Project, I will work with a **AdSmartABdata data** I found on
Kaggle. I intend to run a case study where A/B testing is applied with
different browsers, for different phone types and accros operating
system platofrms. The primary aim is to compare user interactions to
determine which one statistically improves the navigation experience by
increasing our collecting of your bio information in our smart ad.

The Data Columns :

-   **auction_id:** the unique id of the online user who has been
    presented the BIO. In standard terminologies this is called an
    impression id. The user may see the BIO questionnaire but choose not
    to respond. In that case both the yes and no columns are zero. 

-   **experiment:** which group the user belongs to - control or
    exposed.

    -   **control:** users who have been shown a dummy ad

    -   **exposed:** users who have been shown a creative, an online
        interactive ad, with the SmartAd brand. 

-   **date:** the date in YYYY-MM-DD format

-   **hour:** the hour of the day in HH format.

-   **device_make:** the name of the type of device the user has e.g.
    Samsung

-   **platform_os:** the id of the OS the user has.

-   **browser:** the name of the browser the user uses to see the BIO
    questionnaire.

-   **yes:** 1 if the user chooses the "Yes" radio button for the BIO
    questionnaire.

-   **no:** 1 if the user chooses the "No" radio button for the BIO
    questionnaire.

Import packages for the analysis

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
library(tools)
library(scales)
library(broom)
library(MASS)
library(rmarkdown)
library(dplyr)
library(MASS)

```

Firstly, I load the data from my local drive .

```{r}
ad.data<- read_csv("ad_data.csv")

```

```{r}
has.answer <- ad.data|>filter(!(yes == 0 & no == 0))

```

**Choosing a Blocking Vairable/ feature/regressor**

i am following this principle to select a blocking variable\

-   t is included as a factor in the experiment.

-   It is not of primary interest to the experimenter.

-   It affects the dependent variable.

-   It is unrelated to independent variables in the experiment.

```{r}
#possible groups for blocking
unique(has.answer$browser)
print('-----------')
unique(has.answer$device_make)
print('-----------')
unique(has.answer$platform_os)
print('-----------')
unique(has.answer$hour)
```

**Naive EDA**

```{r}
has.answer.1 <- as.data.frame(table(has.answer$experiment, has.answer$yes))
has.answer.1 <- has.answer.1 %>% 
  rename(
    experiment = Var1,
    yes = Var2
    )

names(has.answer)
```

-   The representation of click on the radio button (1) and no
    clicks (0) are imbalanced. Users did not clikc alot. Graphically,
    there are are exposed (treatment) than control.

-   Grouping comparing across confounder `browser` , we observed that
    the level of exposed is consistently higher than control.

```{r}

table(has.answer$yes, has.answer$experiment)

hist_s <-has.answer.1 %>%
  ggplot(aes( x = yes, y = Freq, fill = experiment)) +
  geom_bar(stat = 'identity', position = "dodge")


agg_data.1<-  has.answer %>%
  mutate(experiment = as.factor(experiment)) %>%
  group_by(experiment, device_make, browser,yes) |>
   mutate(props =  n()/nrow(has.answer), cnt = n()) 

hist_s

agg_data.1 %>%
 mutate(yes = as.factor(as.character(yes))) %>%
  ggplot(aes(x = as.factor(browser), y = props, fill = experiment)) +
  geom_bar(position = "dodge", stat = "identity") +
  theme(axis.text.x = element_text(angle = 90)) +
  facet_wrap(~as.factor(yes))


```

**group by popular names**

```{r}
pop_browser <- c('Chrome', 'Facebook', 'Safari', 'Samsung')

grp_browser <-has.answer %>%
  mutate(experiment = as.factor(experiment)) %>%
   mutate(browser_name = case_when(
     str_detect( browser, 'Chrome') ~ "Chrome" , 
     str_detect(browser, 'Facebook') ~ "Facebook" , 
     str_detect( browser, 'Safari') ~ "Safari" , 
     str_detect( browser, 'Samsung') ~ "Samsung" ))
     
grp_browser.1 <-  grp_browser %>%
  mutate(experiment = as.factor(experiment)) %>%
  group_by(experiment, browser_name, yes) |>
   mutate(props =  n()/nrow(has.answer), cnt = n()) 


grp_browser.1 %>%
 mutate(yes = as.factor(as.character(yes))) %>%
  ggplot(aes(x = browser_name, y = props, fill = experiment)) +
  geom_bar(position = "dodge", stat = "identity") +
  theme(axis.text.x = element_text(angle = 90)) +
  facet_wrap(~as.factor(yes))

```

```{r}

hist_s <-has.answer.1 %>%

  ggplot(aes( x = yes, y = Freq, fill = experiment)) +
  geom_bar(stat = 'identity', position = "dodge")


```

```{r}
str(df)
```

```{r}
# drop platform_os, device_make, no

drop_columns <- c( "platform_os", "device_make", "no")
df<- has.answer[,!(names(has.answer) %in% drop_columns)]
```

```{r}
df$yes<- as.factor(as.character(df$yes))

df$experiment <- as.factor(df$experiment)
df$browser <- as.factor(df$browser)
df$days<- difftime(df$date,'2020-07-03' ,units="days")

df$experiment<- fct_relevel(df$experiment, c("control","exposed" ))
#df$browser<- fct_relevel(df$browser,
#                 c("Chrome", "Chrome Mobile WebView","Chrome Mobile",
#                  "Chrome Mobile iOS","Mobile Safari",
#                 "Mobile Safari UI/WKWebView",
#                 "Facebook", "Samsung Internet"))

#df$click_through_rate <- df
```

```{r}
vi.hr.yes<- df
```

Compute the click through rate

```{r}
listde <- c('experiment' , 'browser' ,'yes')
click_df<- df |>dplyr::select(listde)|>
group_by(experiment,browser ) |>
summarize(click_through_rate = round(n()/nrow(df),2))

click_df
```

```{r}
sum(click_df$click_through_rate)
```
